Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2016-05-13 cikm2016/testing.tex
edits to evaluation section.

\subsubsection{NULL Filtering}
Each column was then reduced to a maximum sample set of 32. We excluded domain values that either contain the substring \texttt{NULL}, contain no digits and at most one non-whitespace character (\eg \texttt{" / / "}), or any empirically determined common \texttt{NULL} value (\eg \texttt{0000-00-00}, \texttt{NaN}).
%Columns that had no remaining valid samples were discarded.

@@

\subsubsection{Numeric Timestamps}
After NULL filtering, a common class of date representation (numeric timestamps) remained that was unsuited for parsing via our date format syntax. This included Unix epoch timestamps (expressed as second, millisecond or microsecond counts from \texttt{1970-01-01}) and Microsoft Excel timestamps (expressed fractional days since \texttt{1900-01-01}). A simple test to check that the column was numeric and inside a specific range of values representing recent dates allowed us to tag these columns to avoid analyzing them further (and incidentally to identify them for generating a simple date extraction calculation for the user.)

@@

The error rate reflects the fact that only about $40\%$ of the files have an associated format that parses the non-null values without error. To examine the error rate in greater detail, we turn now to Figure~\ref{fig:mdlerror}.

@@

Some of the dates are clearly just numbers, but our approach is to assume that when the user tells us that the column contains dates we should find the best fit. 
The samples include dates from a wide range of historical sources (\eg Roman pottery dates) so we have elected to defer the semantic identification task to the user.

@@

The initial average parsing speed to compute the ranked set of probable parse trees is $0.93s$, while the average time taken to compute the overall dominant pattern(s) for the entire column of data is $1.4s$. While the natural language parsing implementation is in Python as the NLTK package is easily configurable, we could expect greater speed-up in parsing performance by employing C/C++ CYK parsing libraries.

Out of the $31,546$ files used for testing, the NLP parser identified a dominant format for $26, 534 (84.11\%)$ where $p >= 0.5$. $1634$ unique formats were identified. Figure \ref{fig:NLP1} shows a histogram of the most common formats identified containing \texttt{Year}. There are some variations compared to Figure \ref{fig:mdloutput} including the fact that we are not filtering the results by any error rate in the NLP parsed results.

>>>>

\subsubsection{NULL Filtering}
Each column was then reduced to a maximum sample set of 32. We excluded domain values that either contain the substring \texttt{NULL}, contain no digits and at most one non-whitespace character (\textit{e.g.}, \texttt{" / / "}), or any empirically determined common \texttt{NULL} value (\textit{e.g.}, \texttt{0000-00-00}, \texttt{NaN}).
%Columns that had no remaining valid samples were discarded.

@@

\subsubsection{Numeric Timestamps}
After NULL filtering, a common class of date representation (numeric timestamps) remained that was unsuited for parsing via our date format syntax. This included Unix epoch timestamps (expressed as second, millisecond or microsecond counts from \texttt{1970-01-01}) and Microsoft Excel time-stamps (expressed as fractional days since \texttt{1900-01-01}). A simple test to check that the column was numeric and inside a specific range of values representing recent dates allowed us to tag these columns to avoid analyzing them further (and incidentally to identify them for generating a simple date extraction calculation for the user.)

@@

The error rate reflects the fact that only about $40\%$ of the files have an associated format that parses the non-null values without error. To examine the error rate in greater detail, we refer to Figure~\ref{fig:mdlerror}.

@@

Some of the dates are clearly just numbers, but our approach is to assume that when the user tells us that the column contains dates we should find the best fit. 
The samples include dates from a wide range of historical sources (\textit{e.g.}, Roman pottery dates) so we have elected to defer the semantic identification task to the user.

@@

The initial average parsing speed to compute the ranked set of probable parse trees is $0.93s$, and the average time taken to compute the overall dominant pattern(s) for the entire column of data is $1.4s$. While the natural language parsing implementation is in Python as the NLTK package is easily configurable, we could expect greater speed-up in parsing performance by employing C/C++ CYK parsing libraries.

Out of the $31,546$ files used for testing, the NLP parser identified a dominant format for $26, 534$ ($84.11\%$) where $p >= 0.5$. $1634$ unique formats were identified. Figure \ref{fig:NLP1} shows a histogram of the most common formats identified containing \texttt{Year}. There are some variations compared to Figure \ref{fig:mdloutput} including the fact that we are not filtering the results by any error rate in the NLP parsed results.
